KidsAIR: merge exposure datasets

### 2020-03-27 child_health_data_cleaning.Rmd
New summary plots
merge health data

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 27 Feb 2020"
output: pdf_document 
---

@@

@@

@@

@@

# Waiting on files from NN and AK
```

@@

@@

# Waiting on files from NN and AK
```

>>>>

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 27 March 2020"
output: pdf_document 
---

@@

# Format at-home-log and merge with PM data
```{r}
kids_at_home_log <- read_rds("Output/kids_at_home_log.rds") %>% 
  arrange(area, home_winter_id, at_home_day)

kids_at_home_log_new <- kids_at_home_log %>% 
  mutate(sampling_day = at_home_day) %>% 
  group_by(area, home_winter_id, child_id_num, sampling_day) %>% 
  mutate("00:00:00" = 1,
         "01:00:00" = 1,
         "02:00:00" = 1,
         "03:00:00" = 1,
         "04:00:00" = 1,
         "05:00:00" = 1,
         "06:00:00" = 1,
         "07:00:00" = as.numeric(at_home_7) - 1,
         "08:00:00" = as.numeric(at_home_8) - 1,
         "09:00:00" = as.numeric(at_home_9) - 1,
         "10:00:00" = as.numeric(at_home_10) - 1,
         "11:00:00" = as.numeric(at_home_11) - 1,
         "12:00:00" = as.numeric(at_home_12) - 1,
         "13:00:00" = as.numeric(at_home_13) - 1,
         "14:00:00" = as.numeric(at_home_14) - 1,
         "15:00:00" = as.numeric(at_home_15) - 1,
         "16:00:00" = as.numeric(at_home_16) - 1,
         "17:00:00" = as.numeric(at_home_17) - 1,
         "18:00:00" = as.numeric(at_home_18) - 1,
         "19:00:00" = as.numeric(at_home_19) - 1,
         "20:00:00" = as.numeric(at_home_20) - 1,
         "21:00:00" = as.numeric(at_home_21) - 1,
         "22:00:00" = as.numeric(at_home_22) - 1,
         "23:00:00" = 1) %>% 
  pivot_longer(cols = c("00:00:00":"23:00:00"), names_to = "sample_time",
                        values_to = "at_home") %>% 
  mutate("00:00:00" = "home",
         "01:00:00" = "home",
         "02:00:00" = "home",
         "03:00:00" = "home",
         "04:00:00" = "home",
         "05:00:00" = "home",
         "06:00:00" = "home",
         "07:00:00" = location_7,
         "08:00:00" = location_8,
         "09:00:00" = location_9,
         "10:00:00" = location_10,
         "11:00:00" = location_11,
         "12:00:00" = location_12,
         "13:00:00" = location_13,
         "14:00:00" = location_14,
         "15:00:00" = location_15,
         "16:00:00" = location_16,
         "17:00:00" = location_17,
         "18:00:00" = location_18,
         "19:00:00" = location_19,
         "20:00:00" = location_20,
         "21:00:00" = location_21,
         "22:00:00" = location_22,
         "23:00:00" = "home") %>% 
  select(area, home, home_winter_id, child_id_num, winter_id, treatment,
         sampling_day, sample_time, at_home, "00:00:00":"23:00:00") %>% 
  group_by(area, home_winter_id, child_id_num, sampling_day, sample_time) %>% 
  pivot_longer(cols = c("00:00:00":"23:00:00"), names_to = "location_time",
                        values_to = "at_home_location") %>% 
  mutate(filter_var = if_else(sample_time == location_time, 1, 0)) %>% 
  filter(filter_var == 1) %>%  
  arrange(area, home_winter_id, child_id_num, sampling_day, sample_time) %>% 
  select(area, home, home_winter_id, child_id_num, winter_id, treatment,
         sampling_day, sample_time, at_home, at_home_location)  %>% 
  group_by(area, home_winter_id, child_id_num, sampling_day) %>% 
  mutate(at_home = if_else(sample_time == "06:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "05:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "04:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "03:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "02:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "01:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "00:00:00", lead(at_home), at_home),
         at_home = if_else(sample_time == "23:00:00", lag(at_home), at_home),
         at_home_location = if_else(sample_time == "06:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "05:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "04:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "03:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "02:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "01:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "00:00:00", 
                                    lead(at_home_location), at_home_location),
         at_home_location = if_else(sample_time == "23:00:00", 
                                    lag(at_home_location), at_home_location),
         at_home_location = if_else(at_home == 1, "home", at_home_location)) %>% 
  ungroup() %>% 
  arrange(area, home_winter_id, child_id_num, sampling_day, sample_time)

at_home_pm_merged <- pm_clean %>% 
  group_by(area, home) %>% 
  mutate(pm = if_else(pm > 500, 500, pm),
         pm_mean_sampling_period = mean(pm, na.rm = TRUE)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(pm_mean_sampling_day = mean(pm, na.rm = TRUE),
         pm_datetime_merge = round_date(pm_datetime_new, unit = "hour"),
         pm_obs_sampling_day = n()) %>% 
  separate(pm_datetime_merge, c("sample_date", "sample_time"), sep = " ", remove = FALSE) %>% 
  group_by(area, home, sampling_day, sample_time) %>% 
  mutate(pm_mean_hour = mean(pm, na.rm = TRUE)) %>% 
  distinct(sample_time, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(sampling_day = as.character(sampling_day)) %>% 
  select(area, home, home_winter_id, winter_id, treatment, sampling_day, 
         sample_date, sample_time, pm_mean_hour, pm_mean_sampling_day, 
         pm_mean_sampling_period, day_of_week, pm_obs_sampling_day) %>% 
  left_join(kids_at_home_log_new, 
            by = c("area", "home", "home_winter_id", "winter_id", "treatment",
                   "sampling_day", "sample_time")) %>% 
  group_by(area, home, home_winter_id, child_id_num, at_home) %>% 
  mutate(pm_at_home_sampling_period = mean(pm_mean_hour, na.rm = TRUE)) %>% 
  group_by(area, home, home_winter_id, child_id_num, sampling_day, at_home) %>% 
  mutate(pm_at_home_sampling_day = mean(pm_mean_hour, na.rm = TRUE)) %>% 
  distinct(at_home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  filter(!is.na(at_home)) %>% 
  arrange(area, home_winter_id, child_id_num, at_home, sampling_day)

#write_rds(at_home_pm_merged, "Output/at_home_pm_merged.rds")
#write_csv(at_home_pm_merged, "Output/at_home_pm_merged.csv")

at_home_pm_merged <- read_rds("Output/at_home_pm_merged.rds")
```

@@

kids_med_visit <- read_rds("Output/kids_med_visit.rds")

@@

# Combine logs from all areas
kids_birth_infancy <- wmt_birthinfancy_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

# write_rds(kids_birth_infancy, "Output/kids_birth_infancy.rds")

kids_birth_infancy <- read_rds("Output/kids_birth_infancy.rds")

@@

# Combine logs from all areas
child_home_winter <- wmt_childhomewinter_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

# write_rds(child_home_winter, "Output/child_home_winter.rds")

child_home_winter <- read_rds("Output/child_home_winter.rds")

```

@@

# Combine logs from all areas
kids_csq <- wmt_csq_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

# write_rds(kids_csq, "Output/kids_csq.rds")

kids_csq <- read_rds("Output/kids_csq.rds")

@@

# Combine logs from all areas
kids_medical_records <- wmt_medicalrecords_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

# write_rds(kids_medical_records, "Output/kids_medical_records.rds")

kids_medical_records <- read_rds("Output/kids_medical_records.rds")
```

### 2020-03-27 exposure_models.Rmd
merge health data

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds") 
```

>>>>

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long_new.rds")

exposure_analysis_data_medium <- read_rds("Output/exposure_analysis_data_medium.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds")

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")
```

### 2020-03-27 merge_datasets.Rmd
merge health data

---
title: "KidsAIR: merge datasets"
author: "Ethan Walker"
date: "Started 24 March 2020, Updated 26 March 2020"
output: pdf_document
---

@@

#kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
demographics_clean <- read_rds("Output/demographics_clean.rds")
moisture_clean <- read_rds("Output/moisture_clean.rds")
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
home_char_clean <- read_rds("Output/home_char_clean.rds")
home_act_clean <- read_rds("Output/home_act_clean.rds")
```

@@

save_var_names <- data.frame(t(exposure_analysis_data_long)) %>% 
  rownames_to_column() %>% 
  select(rowname)
write_csv(save_var_names, "Output/kids_data_var_names.csv")
```

@@

exposure_analysis_data_medium <- exposure_analysis_data_long_new %>% 
  select(area, home, home_winter_id, winter_id, treatment, 
         sampling_day, sample_date, burn_level:wood_collect_method_2level) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment, sampling_day,
         child_id_char, burn_level:wood_collect_method_2level) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:wood_collect_method_2level) %>% 
  filter(filter_var == 0)

>>>>

---
title: "KidsAIR: merge exposure datasets"
author: "Ethan Walker"
date: "Started 24 March 2020, Updated 27 March 2020"
output: pdf_document
---

@@

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")
demographics_clean <- read_rds("Output/demographics_clean.rds")
moisture_clean <- read_rds("Output/moisture_clean.rds")
indoor_temp_rh_clean <- read_rds("Output/indoor_temp_rh_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
home_char_clean <- read_rds("Output/home_char_clean.rds")
home_act_clean <- read_rds("Output/home_act_clean.rds")
```

@@

save_var_names <- data.frame(t(exposure_analysis_data_long)) %>% 
  rownames_to_column() %>% 
  select(rowname)

#write_csv(save_var_names, "Output/kids_data_var_names.csv")
```

@@

exposure_analysis_data_medium <- exposure_analysis_data_long_new %>% 
  select(area, home, home_winter_id, winter_id, treatment, 
         sampling_day, sample_date, burn_level:wood_collect_method_2level) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  select(area, home, home_winter_id, winter_id, treatment, sampling_day,
         child_id_char, burn_level:wood_collect_method_2level) %>% 
  mutate(filter_var = if_else(winter_id == 1 & is.na(sampling_day) & lead(sampling_day) == 1, 1, 0),
         filter_var = if_else(is.na(filter_var), 0, filter_var)) %>% 
  select(filter_var, area:wood_collect_method_2level) %>% 
  filter(filter_var == 0) %>% 
  select(-filter_var)
